\newpage
\section*{ecom12-13.pdf}
\textbf{CS/B.TECH/CSE/SEM-8/CS-801E/2013} \\
\textbf{E-COMMERCE AND ERP} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{GROUP - A (Multiple Choice Type Questions)}
1. Choose the correct answers for the following: ($10 \times 1 = 10$)
\begin{enumerate}
    \item[i)] What combines purchase requests from multiple buyers into a single large order, which justifies a discount from the business?
    \begin{enumerate}
        \item[a)] Digital divide
        \item[b)] Global digital divide
        \item[c)] Demand aggregation
        \item[d)] None of these.
    \end{enumerate}
    \item[ii)] Which segment do eBay, Amazon.com and LandsEnd.com belong?
    \begin{enumerate}
        \item[a)] B2Bs
        \item[b)] B2Cs
        \item[c)] C2Bs
        \item[d)] C2Cs.
    \end{enumerate}
    \item[iii)] Digital products are best suited for B2C e-commerce because they
    \begin{enumerate}
        \item[a)] are commodity like products
        \item[b)] can be mass-customized and personalized
        \item[c)] can be delivered at the time of purchase
        \item[d)] all of these.
    \end{enumerate}
    \item[iv)] All of the following are techniques B2C e-commerce companies use to attract customers, except
    \begin{enumerate}
        \item[a)] Registering with search engines
        \item[b)] Viral marketing
        \item[c)] Online ads
        \item[d)] Virtual marketing.
    \end{enumerate}
    \item[v)] What is the percentage of customers who visit a Web site and actually buy something called ?
    \begin{enumerate}
        \item[a)] Affiliate programs
        \item[b)] Click-throughs
        \item[c)] Spam
        \item[d)] Conversion rate.
    \end{enumerate}
    \item[vi)] What are plastic cards of the size of a credit card that contains an embedded chip on which digital information can be stored ?
    \begin{enumerate}
        \item[a)] Customer relationship management systems cards
        \item[b)] E-government identity cards
        \item[c)] FEDI cards
        \item[d)] Smart cards.
    \end{enumerate}
    \item[vii)] Which of the following are advantages normally associated with B2B e-commerce ?
    \begin{enumerate}
        \item[a)] Shorter cycle times
        \item[b)] Reduction in costs
        \item[c)] Reaches wider audiences
        \item[d)] All of these.
    \end{enumerate}
    \item[viii)] If the suppliers in a particular industry hold a lot of power, the industry is
    \begin{enumerate}
        \item[a)] saturated with alternative products or services
        \item[b)] using information technology to gain a competitive advantage
        \item[c)] more attractive to enter
        \item[d)] none of these.
    \end{enumerate}
    \item[ix)] Which statement describes switching costs ?
    \begin{enumerate}
        \item[a)] There are many alternatives to using the product or service
        \item[b)] There are few alternatives to using the product or service
        \item[c)] High costs that make customers reluctant to switch to another product or service
        \item[d)] Low costs that make customers want to switch to another product or service.
    \end{enumerate}
    \item[x)] Which of the following is a useful tool when considering business strategy and IT?
    \begin{enumerate}
        \item[a)] Porter's Five Forces Model
        \item[b)] Competitive Intelligence
        \item[c)] General Business Model
        \item[d)] B2B model.
    \end{enumerate}
\end{enumerate}

\subsection*{GROUP - B (Short Answer Type Questions)}
Answer any three of the following. ($3 \times 5 = 15$)
\begin{enumerate}
    \item[2.] Can ERP software package be applied in 
    i) Process Industry 
    ii) Service Industry? 
    Justify.
    \item[3.] What are the risks for a small company connecting itself electronically with major customers?
    \item[4.] Briefly explain the supply chain planning and a few software for SCP.
    \item[5.] Define WAP. What are the handheld devices?
    \item[6.] What are the advantages and disadvantages of E-Cash ?
\end{enumerate}

\subsection*{GROUP - C (Long Answer Type Questions)}
Answer any three of the following. ($3 \times 15 = 45$)
\begin{enumerate}
    \item[7.] 
    a) What steps are to be followed while implementing IT software packages for SCM? \\
    b) Do these steps vary from package to package? How are they standardized ?
    \item[8.] 
    a) Give a list of potential benefits of using EDI. \\
    b) Who are the service providers of EDI in India and what are their terms and conditions? \\
    c) Compare and contrast Extranet and Intranet.
    \item[9.] 
    a) What are the main disadvantages of E-Commerce ? \\
    b) What are the four C's? Describe briefly with structured diagram what each 'C' means.
    \item[10.] 
    a) Define ERP. Give its tangible and intangible benefits. \\
    b) Why does a company pursue a new ERP solution? \\
    c) What are the functional modules and technical modules in ERP package ?
    \item[11.] Write short notes on any three of the following: ($3 \times 5 = 15$)
    \begin{enumerate}
        \item[a)] B2B
        \item[b)] Data Warehouse
        \item[c)] SCE Framework
        \item[d)] Data Encryption methodology
        \item[e)] Decision Support System.
    \end{enumerate}
\end{enumerate}

\newpage
\section*{ecom13-14.pdf}
\textbf{CS/B.Tech/Even/CSE/8th Sem/CS-802E/2014} \\
\textbf{E-Commerce} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{GROUP - A (Multiple Choice Type Questions)}
1. Choose the correct alternatives for the following: ($10 \times 1 = 10$)
\begin{enumerate}
    \item[i)] EDI requires
    \begin{enumerate}
        \item[a)] representation of common business documents in computer readable form
        \item[b)] data entry operators by receivers
        \item[c)] special value added networks
        \item[d)] special hardware at co-operating business premises.
    \end{enumerate}
    \item[ii)] By security in e-Commerce we mean \\
    I. protecting an organization's data resource from unauthorized access \\
    II. preventing disasters from happening \\
    III. authenticating messages received by an organization \\
    IV. protecting messages sent on the Internet from being read and understood by unauthorized persons/organizations
    \begin{enumerate}
        \item[a)] I, III
        \item[b)] II, III
        \item[c)] III, IV
        \item[d)] I, III, IV
    \end{enumerate}
    \item[iii)] A firewall may be implemented in
    \begin{enumerate}
        \item[a)] routers which connect Intranet to internet
        \item[b)] bridges used in an Intranet
        \item[c)] expensive modem
        \item[d)] user's application programs.
    \end{enumerate}
    \item[iv)] Public key encryption method is a system
    \begin{enumerate}
        \item[a)] which uses a set of public keys one for each participant in e-commerce
        \item[b)] in which each person who wants to communicate has two keys: a private key known to him only and a public key which is publicized to enable others to send message to him
        \item[c)] which uses the RSA coding system
        \item[d)] which is a standard for use in e-Commerce.
    \end{enumerate}
    \item[v)] In electronic cash payment \\
    I. a customer withdraws 'coins' in various denominations signed by the bank \\
    II. the bank has a database of issued coins \\
    III. the bank has a database of spent coins \\
    IV. the bank cannot trace a customer.
    \begin{enumerate}
        \item[a)] I, II
        \item[b)] I, II, III
        \item[c)] I, II, III, IV
        \item[d)] II, III, IV
    \end{enumerate}
    \item[vi)] SET protocol is use for
    \begin{enumerate}
        \item[a)] Securing message transfer
        \item[b)] Securing card transaction
        \item[c)] Securing authentication
        \item[d)] Securing overall e-Commerce
    \end{enumerate}
    \item[vii)] A key is a
    \begin{enumerate}
        \item[a)] Value
        \item[b)] Logic
        \item[c)] Function
        \item[d)] All of these
    \end{enumerate}
    \item[viii)] Which modal of e-commerce deals with virtual auction?
    \begin{enumerate}
        \item[a)] Aggregator model
        \item[b)] Community model
        \item[c)] Info-mediary model
        \item[d)] Brokerage model.
    \end{enumerate}
    \item[ix)] A/An \underline{\hspace{2cm}} is a network that links selected resources of a company's internet with its customers, suppliers or other business partners.
    \begin{enumerate}
        \item[a)] internet
        \item[b)] extranet
        \item[c)] VPN
        \item[d)] wide area network
    \end{enumerate}
    \item[x)] How many types of trade cycle are there in e-commerce?
    \begin{enumerate}
        \item[a)] One
        \item[b)] Two
        \item[c)] Three
        \item[d)] Four
    \end{enumerate}
\end{enumerate}

\subsection*{GROUP - B (Short Answer Type Questions)}
Answer any three of the following. ($3 \times 5 = 15$)
\begin{enumerate}
    \item[2.] What do you mean by knowledge engineering and business process redesign?
    \item[3.] Explain E-Governance with suitable examples.
    \item[4.] What are the benefits and points of concern in CPD?
    \item[5.] What is BPR? Explain with an example.
    \item[6.] Distinguish between CRM and SRM.
\end{enumerate}

\subsection*{GROUP - C (Long Answer Type Questions)}
Answer any three of the following questions. ($3 \times 15 = 45$)
\begin{enumerate}
    \item[7.] 
    a) What is Digital signature? How they differ from Digital certificate? \\
    b) Given two prime nos. $P=17$, $Q=29$. Find out N, E and D in RSA encryption. \\
    c) What is firewall? State the function of firewall in e-commerce.
    \item[8.] 
    a) What is call center? Discuss about the call center equipment. \\
    b) What are the modes of operation of call center? \\
    c) What is Customer Premises Equipment (CPE)? What do you mean by Denial of Service Attacks?
    \item[9.] 
    a) What is EDI ? \\
    b) What are the basic components of EDI? Describe briefly. \\
    c) What role does it play in e-commerce ? \\
    d) Explain EDIFACT. \\
    e) Briefly explain the benefits of EDI
    \item[10.] 
    a) Define ERP. How can information be integrated using ERP? \\
    b) What are the reasons for the growth of ERP market? What are the advantages of ERP system?
    \item[11.] Write short notes on any three of the following: ($3 \times 5 = 15$)
    \begin{enumerate}
        \item[a)] EAI
        \item[b)] SCE framework
        \item[c)] BAAN
        \item[d)] SAP
        \item[e)] VPN
    \end{enumerate}
\end{enumerate}

\newpage
\section*{ecom14-15.pdf}
\textbf{CS/B.Tech/CSE/Even/Sem-8th/CS-802E/2015} \\
\textbf{E-COMMERCE (IT)} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{GROUP A (Multiple Choice Type Questions)}
1. Answer all questions. ($10 \times 1 = 10$)
\begin{enumerate}
    \item[i)] Electronic Commerce is commerce enabled by
    \begin{enumerate}
        \item[A)] EDP era technologies
        \item[B)] MIS era technologies
        \item[C)] Internet era technologies
        \item[D)] All of these
    \end{enumerate}
    \item[ii)] SHA is more secure than MD5 by the factor of
    \begin{enumerate}
        \item[A)] $2^{16}$
        \item[B)] $2^{64}$
        \item[C)] $2^{8}$
        \item[D)] $2^{32}$
    \end{enumerate}
    \item[iii)] In EAN coding system, within the EAN code manufacturer is of \underline{\hspace{1cm}} bit/s and check digit is of \underline{\hspace{1cm}} bit/s.
    \begin{enumerate}
        \item[A)] 4, 2
        \item[B)] 3, 3
        \item[C)] 5, 1
        \item[D)] 1, 4
    \end{enumerate}
    \item[iv)] Friction in a transaction is defined as
    \begin{enumerate}
        \item[A)] overhead
        \item[B)] loss
        \item[C)] profit
        \item[D)] none of these
    \end{enumerate}
    \item[v)] If $Z=160$ and $E=7$, then for what value of D, $(ED \mod z = 1)$ will be satisfied?
    \begin{enumerate}
        \item[A)] 33
        \item[B)] 22
        \item[C)] 45
        \item[D)] 23
    \end{enumerate}
    \item[vi)] 'Flood Attack' by attackers happens on
    \begin{enumerate}
        \item[A)] router
        \item[B)] hub
        \item[C)] switch
        \item[D)] server
    \end{enumerate}
    \item[vii)] "Mouse Rollover Effect" is the example of
    \begin{enumerate}
        \item[A)] Server Side Scripting
        \item[B)] Client Side Scripting
        \item[C)] Both (A) and (B)
        \item[D)] None of these
    \end{enumerate}
    \item[viii)] Which of the following is ASCII protocol?
    \begin{enumerate}
        \item[A)] SNMP
        \item[B)] SMTP
        \item[C)] SET
        \item[D)] PGP
    \end{enumerate}
    \item[ix)] Use the SHIFT CIPHER with key $=17$ to encrypt the message "WBUT". The cipher text will be
    \begin{enumerate}
        \item[A)] XCVU
        \item[B)] NSLK
        \item[C)] ALSEC
        \item[D)] KLMPN
    \end{enumerate}
    \item[x)] Which of the following card contains a microprocessor and a storage unit?
    \begin{enumerate}
        \item[A)] Smart Card
        \item[B)] Debit Card
        \item[C)] Credit Card
        \item[D)] None of these
    \end{enumerate}
\end{enumerate}

\subsection*{GROUP B (Short Answer Type Questions)}
Answer any three questions. ($3 \times 5 = 15$)
\begin{enumerate}
    \item[2.] What is E-business? How does it help the marketing? Write down various advantages of e-business?
    \item[3.] Explain about Internet, Intranet \& Extranet.
    \item[4.] What do you mean by online payment? How does it differ from e-payment?
    \item[5.] What is firewall? What do you know about DNS?
    \item[6.] Write short notes on any three of the following:
    \begin{enumerate}
        \item[a)] Copyright
        \item[b)] E-governance
        \item[c)] Smart Card
        \item[d)] E-mail
        \item[e)] HTML
    \end{enumerate}
\end{enumerate}

\subsection*{GROUP C (Long Answer Type Questions)}
Answer any three questions. ($3 \times 15 = 45$)
\begin{enumerate}
    \item[7.] What do you know about e-cash? What is digital signature? How it relates with e-commerce? What do you mean by digital library? Write down the application of digital library.
    \item[8.] What is EDI? How EDI works? Explain with diagram. Write down the advantages of EDI. How does it help e-commerce business strategy?
    \item[9.] What is tele marketing \& online marketing? How e-commerce differs from m-commerce? What do you know about supply chain management? How it relates with e-commerce?
    \item[10.] What is cryptography? Explain various types of cryptography. Why cryptography is needed for e-commerce? What do you know about RSA algorithm? Explain.
\end{enumerate}

\newpage
\section*{ecom15-16.pdf}
\textbf{CS/B.TECH/CSE/EVEN/SEM-8/CS-802E/2015-16} \\
\textbf{E-COMMERCE} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{GROUP - A (Multiple Choice Type Questions)}
1. Choose the correct alternatives for the following: ($10 \times 1 = 10$)
\begin{enumerate}
    \item[i)] Which one of the following is not an E-Commerce ?
    \begin{enumerate}
        \item[a)] B2C
        \item[b)] B2G
        \item[c)] B2D
        \item[d)] B2B.
    \end{enumerate}
    \item[ii)] The default port of HTTP is
    \begin{enumerate}
        \item[a)] 81
        \item[b)] 80
        \item[c)] 70
        \item[d)] 71.
    \end{enumerate}
    \item[iii)] ISP stands for
    \begin{enumerate}
        \item[a)] Internet Service Provider
        \item[b)] Internet Service Protocol
        \item[c)] Intranet Service Protocol
        \item[d)] none of these.
    \end{enumerate}
    \item[iv)] Electronic commerce is enabled by
    \begin{enumerate}
        \item[a)] EDP era technologies
        \item[b)] MIS era technologies
        \item[c)] Internet era technologies
        \item[d)] all of these.
    \end{enumerate}
    \item[v)] Friction in a transaction is defined as
    \begin{enumerate}
        \item[a)] overhead
        \item[b)] loss
        \item[c)] profit
        \item[d)] none of these.
    \end{enumerate}
    \item[vi)] Flood attack by attackers happens on
    \begin{enumerate}
        \item[a)] router
        \item[b)] hub
        \item[c)] switch
        \item[d)] server.
    \end{enumerate}
    \item[vii)] Which one of the following is ASCII protocol ?
    \begin{enumerate}
        \item[a)] SNMP
        \item[b)] SMTP
        \item[c)] SET
        \item[d)] PGP.
    \end{enumerate}
    \item[viii)] Credit Card payment is under
    \begin{enumerate}
        \item[a)] B2B e-commerce
        \item[b)] B2C e-commerce
        \item[c)] C2C e-commerce
        \item[d)] none of these.
    \end{enumerate}
    \item[ix)] E-trading is also called
    \begin{enumerate}
        \item[a)] E-brokering
        \item[b)] E-supply
        \item[c)] E-auctions
        \item[d)] both (a) and (b).
    \end{enumerate}
    \item[x)] DES stands for
    \begin{enumerate}
        \item[a)] Data Encryption Standard
        \item[b)] Digital Encryption Standard
        \item[c)] Double Encryption Standard
        \item[d)] Data Encryption System.
    \end{enumerate}
\end{enumerate}

\subsection*{GROUP B (Short Answer Type Questions)}
Answer any three of the following. ($3 \times 5 = 15$)
\begin{enumerate}
    \item[2.] Define Electronic Data Interchange. What are the components of Electronic Data Interchange ?
    \item[3.] Explain how SSL protocol is used for secure transaction. Explain the advantages of e-commerce.
    \item[4.] Discuss in brief virtual auction. Explain the differences between virtual auction and reverse auction.
    \item[5.] What is Firewall? State the function of Firewall in e-commerce.
    \item[6.] What role does SCM play in Business to Business model i.e. B2B e-commerce ?
\end{enumerate}

\subsection*{GROUP-C (Long Answer Type Questions)}
Answer any three of the following. ($3 \times 15 = 45$)
\begin{enumerate}
    \item[7.] Explain the different types of digital documents. How risk is handled in e-Payment system? Explain how Smart Cards and Credit Cards have roles in e-commerce applications.
    \item[8.] Describe the functional requirements for online selling and what specialized services and servers perform these functions. Who are the stakeholders in e-commerce information system? Explain the benefits and limitations of e-commerce. Explain the concept of 'Business Content' in SAP Business Information Warehouse.
    \item[9.] 
    a) Define digital cash or e-cash. Explain with example how an online banking system works. \\
    b) Explain the working principle of DES algorithm.
    \item[10.] Distinguish between SSL and SET protocol. Explain EAN coding system for EDI message. Explain the ways and means of protecting online website operations from hackers.
    \item[11.] Write short notes on any three of the following: ($3 \times 5 = 15$)
    \begin{enumerate}
        \item[a)] RSA algorithm
        \item[b)] Trade cycle and different stages of a Trade cycle
        \item[c)] Data Warehouse
        \item[d)] Decision support system
        \item[e)] Collaborative computing.
    \end{enumerate}
\end{enumerate}