\newpage
\section*{ecom22-23.pdf}
\textbf{CS/B.TECH(N)/EVEN/SEM-8/8261/2022-2023/1124} \\
\textbf{MAULANA ABUL KALAM AZAD UNIVERSITY OF TECHNOLOGY, WEST BENGAL} \\
\textbf{Paper Code: OEC-CS802A/OECIT802A \hfill E-Commerce and ERP} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{Group-A (Very Short Answer Type Question)}
1. Answer any ten of the following: ($1 \times 10 = 10$)
\begin{enumerate}
    \item[(I)] What is 'EOQ' in Inventory control?
    \item[(II)] What is URL?
    \item[(III)] Compared to B2C e-commerce, B2B e-commerce is \underline{\hspace{2cm}}
    \item[(IV)] What is email marketing?
    \item[(V)] EDI stands for \underline{\hspace{2cm}}
    \item[(VI)] VMI stands for \underline{\hspace{2cm}}
    \item[(VII)] What type of E-Commerce is tenders and submission of application?
    \item[(VIII)] What is called sale or purchase of items without physically visiting a shop?
    \item[(IX)] What is E-Business?
    \item[(X)] The purchase of machinery, equipment, or materials must go through the \underline{\hspace{2cm}} department.
    \item[(XI)] What is a virtual storefront?
    \item[(XII)] SMTP refers to \underline{\hspace{2cm}}
\end{enumerate}

\subsection*{Group-B (Short Answer Type Question)}
Answer any three of the following: ($5 \times 3 = 15$)
\begin{enumerate}
    \item[2.] What are the 4 C's of Digital Marketing?
    \item[3.] Explain the Internet Marketing in detail.
    \item[4.] What are the features of E-commerce?
    \item[5.] Discuss EDI architecture.
    \item[6.] Explain the internet industry structure with diagram?
\end{enumerate}

\subsection*{Group-C (Long Answer Type Question)}
Answer any three of the following: ($15 \times 3 = 45$)
\begin{enumerate}
    \item[7.] 
    (a) Write down the benefits of electronic web commerce. [5] \\
    (b) Distinguish between Internet and Intranet. [5] \\
    (c) What is Firewall? [3] \\
    (d) What do you mean by Electronic Marketers? [2]
    \item[8.] 
    (a) Explain any 5 types of Electronic Payment Systems. [10] \\
    (b) Discuss the impact of e-commerce in the following areas: [5] \\
    (i) Marketing \\
    (ii) Finance and Accounting
    \item[9.] 
    (a) Define Convergence, Collaborative Computing, Content Management \& Call Center. [10] \\
    (b) How is e-mail useful for E-Commerce? Is it secure to transact through e-mail? Explain and justify. [5]
    \item[10.] 
    (a) Distinguish between e-business and e-commerce. [5] \\
    (b) Discuss how E-Commerce is helpful to business success. [5] \\
    (c) Write about Tangible and Intangible benefits of e-business. [5]
    \item[11.] 
    (a) Draw and explain the architecture of an online shopping e-commerce portal that sells a large number of different types of goods. [10] \\
    (b) Discuss how E-Commerce is helpful to business success. [5]
\end{enumerate}


\newpage
\section*{ecom23-24.pdf}
\textbf{CS/B.TECH(N)/EVEN/SEM-8/8261/2023-2024/1019} \\
\textbf{MAULANA ABUL KALAM AZAD UNIVERSITY OF TECHNOLOGY, WEST BENGAL} \\
\textbf{Paper Code: OEC-CS802A/OECIT802A \hfill E-Commerce and ERP} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{Group-A (Very Short Answer Type Question)}
1. Answer any ten of the following: ($1 \times 10 = 10$)
\begin{enumerate}
    \item[(I)] Name programming languages used to develop web applications.
    \item[(II)] Explain the meaning of E-procurement.
    \item[(III)] Give an example where social media is used as a strategic tool for enhancing E-commerce business.
    \item[(IV)] What do you mean by Collaborative Computing?
    \item[(V)] How do large companies monitor and track cargo deliveries to their customers?
    \item[(VI)] Give an idea about 'Stored-value card'.
    \item[(VII)] What is the full form of VAN and what purpose is it used for?
    \item[(VIII)] Explain what do you mean by 'certificate revocation list (CRL)'.
    \item[(IX)] Give two applications of E-Commerce.
    \item[(X)] Give two applications of M-Commerce.
    \item[(XI)] What according to you should be the ethical principles of E-Commerce?
    \item[(XII)] Give an example in which an e-business focuses on brand identity as a strategy for their online business performance.
\end{enumerate}

\subsection*{Group-B (Short Answer Type Question)}
Answer any three of the following: ($5 \times 3 = 15$)
\begin{enumerate}
    \item[2.] Explain with an example how cart reminders can be used for E-marketing. [5]
    \item[3.] Identify the different steps in EDI implementation. [5]
    \item[4.] Discuss the threats of E-Commerce. [5]
    \item[5.] Discuss the different ways by which the Internet helps E-Commerce. [5]
    \item[6.] Explain the meaning of Customer-premises equipment or customer-provided equipment (CPE). Give examples. [5]
\end{enumerate}

\subsection*{Group-C (Long Answer Type Question)}
Answer any three of the following: ($15 \times 3 = 45$)
\begin{enumerate}
    \item[7.] 
    (a) Discuss the different E-Commerce business models based on transaction type. [8] \\
    (b) Give examples of the business models (based on transaction type) that you have mentioned. [4] \\
    (c) Outline the challenges of E-Governance in India. [3]
    \item[8.] 
    (a) What do you think is Supply Chain Management? [5] \\
    (b) Discuss the merits of implementing an ERP system before Supply Chain. [5] \\
    (c) Discuss the benefits of integrating Supply Chain and ERP systems. [5]
    \item[9.] 
    (a) Discuss the security issues related to E-payments. [9] \\
    (b) Discuss your ideas about cryptocurrency as an e-payment mechanism. [6]
    \item[10.] 
    (a) Discuss the different E-Commerce marketing strategies. [6] \\
    (b) Explain in detail how you will do E-marketing for your online bookstore. [9]
    \item[11.] 
    (a) Differentiate between public key and private key cryptography. [5] \\
    (b) Outline the different services provided by SSL. [5] \\
    (c) Write the algorithm of RSA. [5]
\end{enumerate}


\newpage
\section*{ecom24-25.pdf}
\textbf{CS/B.TECH(N)/EVEN/SEM-8/8261/2024-2025/1130} \\
\textbf{MAULANA ABUL KALAM AZAD UNIVERSITY OF TECHNOLOGY, WEST BENGAL} \\
\textbf{Paper Code: OEC-CS802A/OECIT802A \hfill E-Commerce and ERP} \\
\textbf{Time Allotted: 3 Hours \hfill Full Marks: 70}

\subsection*{Group-A (Very Short Answer Type Question)}
1. Answer any ten of the following: ($1 \times 10 = 10$)
\begin{enumerate}
    \item[(I)] SET protocol is used for \underline{\hspace{2cm}}
    \item[(II)] What type of ad appears on top of a web page?
    \item[(III)] What is the name of the card which can be used by the buyers during the purchase and in which the amount will be immediately debited from the buyer's account?
    \item[(IV)] What is the name for direct computer-to-computer transfer of transaction information contained in standard business documents?
    \item[(V)] What is e-business?
    \item[(VI)] OLX is an example of \underline{\hspace{2cm}} E-commerce segment.
    \item[(VII)] \underline{\hspace{2cm}} type of E-Commerce has trade and transaction dealings between business establishments.
    \item[(VIII)] SCM is a game of 4 C's Collaboration, Co-operation, Co-ordination and \underline{\hspace{2cm}}
    \item[(IX)] What is the full form of CGI?
    \item[(X)] What is the purpose of supply chain management?
    \item[(XI)] What are the characteristics of Digital Cash?
    \item[(XII)] What is virtual store front?
\end{enumerate}

\subsection*{Group-B (Short Answer Type Question)}
Answer any three of the following: ($5 \times 3 = 15$)
\begin{enumerate}
    \item[2.] What are digital signatures? How do they differ from digital certificates? [5]
    \item[3.] What are the main disadvantages of E-Commerce? [5]
    \item[4.] Compare and contrast Extranet and Intranet. [5]
    \item[5.] Describe the advantages and disadvantages of E-marketing over normal marketing. [5]
    \item[6.] What are the key technologies of B2B E-Commerce. Explain the architectural model of B2B E-Commerce. [5]
\end{enumerate}

\subsection*{Group-C (Long Answer Type Question)}
Answer any three of the following: ($15 \times 3 = 45$)
\begin{enumerate}
    \item[7.] 
    (a) What do you mean by supply chain of E-commerce? [2] \\
    (b) Why is Supply Chain Management vital for E-commerce? [3] \\
    (c) Explain the role played by E-supply Chain planning tools in managing the supply chain of an E-business. [5] \\
    (d) How does supply chain management portals help E-commerce in managing supply chain? [5]
    \item[8.] 
    (a) Define firewall and state its functions in e-commerce. [5] \\
    (b) Explain the working principle of RSA algorithm. [5] \\
    (c) What is e-cash ? Explain with example how an online banking system works. [5]
    \item[9.] 
    (a) What is ERP? Why BPR is required prior to ERP implementation? [4] \\
    (b) What are the reasons for the growth of ERP market? [5] \\
    (c) What are the advantages of ERP system? [6]
    \item[10.] 
    (a) What is call center? Discuss about the call center equipment. [5] \\
    (b) What are the modes of operation of call center? [5] \\
    (c) What is customer premises equipment(CPE)? What do mean by Denial of Service attacks ? [5]
    \item[11.] 
    (a) What is EDI? [1] \\
    (b) Briefly describe the basic components of EDI. [4] \\
    (c) What role does it play in E commerce? [4] \\
    (d) Explain EDIFACT. [4] \\
    (e) Write the benefits of EDI. [2]
\end{enumerate}